Diagnostic Plots

### 2024-08-11 pre_print_manuscript.qmd
Add mixture models for p-hacking

In addition to this we also examined both the mixture model for *p*-hacking [@mossModellingPublicationBias2023] and RoBMA [@@bartosRobustBayesianMetaanalysis2023] (both with, and without, the inclusion of an informative prior on the intervention effect from Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011]) though ignored the hierarchical structure to the data. The mixture model for for *p*-hacking provides an adjusted estimate of the intervention effect under the assumption that *p*-hacking such as excluding observations, collecting new data *ex-post*, or selectively including covariates has occured to produce the effects we see in the literature. The RoBMA fits a total of 36 different models with varying assumptions regarding the true data generating process underlying the included studies/effects and thus reflecting our uncertainty in it: selection models varying sidedness of the tests (one- or two-sided) and the specific *p*-value cutoffs used (combinations of 0.025, 0.05, 0.10, and 0.50), the PET-PEESE regression based models, assuming there is/is not an intervention effect, assuming there is/is not heterogeneity, and assuming there is/is not publication bias. These models are then combined using Bayesian model-averaging and weighted based on how well the model fit the data. Bayes Factors were then calculated to examine the evidence in favour of there being an effect, the presence of heterogeneity, and publication bias.

>>>>

In addition to this we also examined both the mixture model for *p*-hacking [@mossModellingPublicationBias2023] and RoBMA [@@bartosRobustBayesianMetaanalysis2023] (both with, and without, the inclusion of an informative prior on the intervention effect from Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011]) though ignored the hierarchical structure to the data. The mixture model for for *p*-hacking provides an adjusted estimate of the intervention effect under the assumption that *p*-hacking such as excluding observations, collecting new data *ex-post*, or selectively including covariates has occurred to produce the effects we see in the literature. The RoBMA fits a total of 36 different models with varying assumptions regarding the true data generating process underlying the included studies/effects and thus reflecting our uncertainty in it: selection models varying sidedness of the tests (one- or two-sided) and the specific *p*-value cutoffs used (combinations of 0.025, 0.05, 0.10, and 0.50), the PET-PEESE regression based models, assuming there is/is not an intervention effect, assuming there is/is not heterogeneity, and assuming there is/is not publication bias. These models are then combined using Bayesian model-averaging and weighted based on how well the model fit the data. Bayes Factors were then calculated to examine the evidence in favour of there being an effect, the presence of heterogeneity, and publication bias.
